Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2018-12-11 paper/snakemajoranas.tex
fixed merge conflict

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
A magnetic field pointed along the x direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Numerical bandstructures
%%██████████████████████████████████████████████████████████████████████████
\section{Numerical bandstructures}

\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian and zigzag geometry.}

\comment{We discretize the model and simulate it with Kwant.}

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}
In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
As the zigzag introduces super cell, we see a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased tenfolds.
We claim this effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
This has an effect on the Majorana coherence length, as described later on in the manuscript.

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
We consider a system (Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
As seen in the figure, we modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth snake like shape.
Just as the normal system[\cite{pientka2017topological}], a magnetic field pointed along the x direction is applied.
We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has Rashba spin-orbit coupling and a Zeeman field, and apart from the kinetic term, the superconductors only have a superconducting term differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
We know from \onlinecite{pientka2017topological} that the non-zigzag system is in class BDI.
Using the software package Qsymm\cite{varjas2018qsymm}, we evaluate the symmetry class of the system to be D.

@@

%%██████████████████████████████████████████████████████████████████████████
%%██ Calculating the bandstuctures
%%██████████████████████████████████████████████████████████████████████████
\section{Calculating the bandstuctures.}

\comment{We consider a 2D SNS junction with a Rashba-BdG Hamiltonian.}
We consider the model described in section II; a two dimensional SNS junction with a Rashba BdG Hamiltonian.

\comment{We discretize the model and simulate it with Kwant.}
In figure \ref{fig:bandstuctures}, We calculate the bandstructure for a zigzag system with varying amplitude using Kwant.
As the zigzag introduces super cell, we see a folded bandstructure.
For comparisons sake, we take the same cell size for the ribbon structure so the bandstructure is folded in the same way.
The introduction of a zigzag has a striking effect: the bands flatten out, and more importantly, the gap size is increased more than an order of magnitude.
This effect is due to the fact that the modes where the gap is smallest, when the momentum is almost completely focused along the strip ($k_x=k_F$), are cut off by the zigzag geometry.
Additionally in the presence of normal reflection, due to the availability of NS interfaces at a wide range of slopes, the reflected part will eventually ``find'' a surface with which it is perpendicular to.
Also apparent is the reduction of group velocity; the slope of the bands is greatly reduced.
This has an effect on the Majorana coherence length, as described later on in the manuscript.
